Appendix

### 2020-10-31 manuscript/article.tex
emphasise causal designs

\begin{abstract}
\noindent In a seminal article, \citet{weingast1981political} argue that there
is a positive relationship between legislature size and inefficiency in public
expenditures. Their proposition is currently known as the ``law of $1/n$'' and
has been widely cited by scholars in political science and public
administration. However, recent studies have questioned the validity of the
theory. In this letter, we estimate the first meta-analysis of the relationship
between the number of legislators and public spending. Based on a sample of 26
empirical studies, we find little effect of legislature size on government
budgets. The available evidence suggests that, if such an effect exists, it is
driven by an increase in the upper chamber, but there is considerable
heterogeneity in the results. Our meta-regressions also indicate that study
coefficients vary significantly according to modelling specifications, such as
estimation method or variable selection.

@@

Aggregate results show that council size has no significant impact on public
spending. Both the meta-analyses and the meta-regressions indicate that we
cannot generalise either the ``law of $1/n$'' or the ``reverse law of $1/n$''.
We find stronger evidence in favour of a positive impact of upper house size on
public budgets, yet the findings are not consistent in all of our estimations.
Our meta-regressions suggest that our study sample has a high level of
heterogeneity, and effects may differ substantially according to research design
specifications. We also find that recent studies, mainly those which employ
regression discontinuity designs, are more likely to find a negative association
between larger legislatures and public spending. In summary, our results point
out that if legislature size affects government budgets, they do so under
specific conditions and are mediated by domestic factors.

>>>>

\begin{abstract}

\noindent In a seminal article, \citet{weingast1981political} argue that there
is a positive relationship between legislature size and inefficiency in public
expenditures. Their proposition is currently known as the ``law of $1/n$'' and
has been widely debated in political science and public administration.
However, recent studies have questioned the validity of the theory. In this
letter, we estimate the first meta-analysis of the relationship between the
number of legislators and public spending. Based on a sample of \textbf{XX}
articles, we find only mixed evidence for the effect of legislature size on
government budgets. Yet the aggregate results mask important differences. While
earlier, non-causal studies provide moderate support for the ``law of $1/n$'',
recent papers using causal inference methods consistently find a negative
relation between seats and spending, suggesting that previous results might
have been driven by spurious correlations or omitted variable bias. The
available evidence also indicates that XXXXXXXXXXXXXXXX

@@

Aggregate results show that council size has no significant impact on public
spending. However, the meta-regressions suggest that our study sample has high
levels of heterogeneity, and effects differ substantially according to research
design specifications. Whereas earlier studies employing convention spending
regressions often find a positive relation between legislature size and
government budgets, recent studies that use new methods of causal inference,
specially those with regression discontinuity designs, provide consistent
evidence for a negative relation. This goes in contrast with the original
theory and supports the existence of a ``reverse law of $1/n$''.
\textbf{Moreover, ...}  In summary, our results point out that if legislature
size affects government budgets, they do so under specific conditions and are
mediated by domestic factors.
